A biometric analysis of infant mortality and temperature, northern Sweden 1895-1950

### 2022-01-16 paper.Rmd
play around ...

```{r neoanal, results = 'asis'}
neo <- age.window(infdat, c(0, 28 /365))
neo$exit <- g(neo$exit * 365)
neo$enter <- g(neo$enter * 365)
fit.ph <- coxreg(Surv(enter, exit, event) ~  socStatus + illeg + parity + period + socBranch  + cold + emintemp + subreg + season,
                 data = neo[neo$sex == "girl", ])
dr <- drop1(fit.ph, test = "Chisq")
ltx(fit.ph, dr = dr, caption = "Neonatal mortality, girls.", label = "tab:neonatal")
```

>>>>

```{r neoanal, results = 'asis'}
neo <- age.window(infdat, c(0, 28 /365))
neo$exit <- g(neo$exit * 365)
neo$enter <- g(neo$enter * 365)
fit.ph <- coxph(Surv(enter, exit, event) ~  socStatus + illeg + parity + period + socBranch  + cold + emintemp + subreg + season,
                 data = neo[neo$sex == "girl", ])
dr <- drop1(fit.ph, test = "Chisq")
ltx(fit.ph, dr = dr, caption = "Neonatal mortality, girls.", label = "tab:neonatal")
```
